---
title: "DanielVas04022022"
author: "Network"
date: "04/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("bootnet") #https://cran.r-project.org/web/packages/bootnet/index.html
#install.packages("qgraph") #https://cran.r-project.org/web/packages/qgraph/index.html
#install.packages("glasso") #https://cran.r-project.org/web/packages/glasso/index.html
#install.packages("codebook") #https://cran.r-project.org/web/packages/glasso/index.html
#install.packages("psychTools")
```

```{r echo=FALSE, warning=FALSE,  include = FALSE}
library(tidyverse)
library(bootnet)
library(qgraph)
library (haven)
```
Data loading

```{r}
data<-haven::read_sav("dataset.sav")%>%
  mutate_if(is.character, as.factor) 
data_sna<- data%>%
  select(GamingTotal, Depression, Anxiety, Stress)
```
The variables of interest for the user avatar bond are the following:

**GamingTotal**= Internet Gaming Disorder Symptoms Total 

**Depression**= Low Mood 
**Anxiety**= Anxious symptoms assessed via DASS-21

**Stress**= Stress symptoms assessed via DASS-21


```{r warning=FALSE}
#estimated network
network <- estimateNetwork(data_sna, 
                           default = "EBICglasso",
                           corMethod = "cor_auto",
                           tuning = 0.5)
print(network)
plot(network, layout='spring')
network$graph
```


centrality
```{r}
centrality(network)
centralityPlot(network)
```
Simulation

```{r}
simRes <- netSimulator(network$graph,
                       dataGenerator = ggmGenerator(
                         ordinal =TRUE, 
                         nLevels = 5),
                       default = "EBICglasso",
                       nCases = c(100,250,500,1000,2500),
                       tuning = 0.5,
                       nReps = 100,
                       nCores = 8)
simRes
plot(simRes)
plot(simRes,yvar = c("strength","closeness","betweenness"))
```



```{r}
boot1 <- bootnet(network, nCores = 8, nBoots = 1000, type = "nonparametric")
boot2 <- bootnet(network, nCores = 8, nBoots = 1000, type = "case")